---
title: "marriage"
subtitle: "My subtitle if needed"
author: 
  - qizhou xie
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)

data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))

```


# Introduction

You can and should cross-reference sections and sub-sections. We use @talia, @opendatatorotno, and @rohan.

The remainder of this paper is structured as follows. @sec-mydatasection



# Data {#sec-mydatasection}

Some of our data is of penguins (@fig-marriage), from @marriage.

```{r}
#| label: fig-marriage
#| fig-cap: Number of marriage license across the years
#| echo: false

data |> 
  ggplot(aes(x = date, y = marriage_licenses)) +
  geom_point()

```






# Discussion

## First discussion point {#sec-first-point}

Overall, there was an effect of covid to the number of marriage licenses during 2020-2021.

\newpage

\appendix

# Appendix {-}


# Additional data details



\newpage


# References


